RE: Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems

### 2023-05-16 rmd/manuscript.Rmd
edit: text

---
title: "Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems"
output: 
  # word_document:
  #   reference_docx: "word_format.docx"
  pdf_document:
   latex_engine: xelatex
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
bibliography: references.bib
csl: https://www.zotero.org/styles/ecosphere
mainfont: Times New Roman
header-includes:
  \usepackage{lineno, textgreek}
  \linenumbers
---

@@

More recently, food web ecologists have begun to recognize that FCL rarely responds to a single driver, but instead is determined by interactions of extrinsic (external environmental conditions) and intrinsic factors (species and/or food web attributes). For example, @wardMechanisticTheoryAquatic2017 showed that FCL was more responsive to increasing productivity in large ecosystems than small ones, whereas FCL was more sensitive to size in low-productivity systems. Such context-dependent responses to extrinsic factors seem to be tightly coupled with the arrangement of trophic links within a food web. For example, omnivory (feeding at multiple trophic levels) is a strong intrinsic driver of FCL [@takimotoEffectsProductivityDisturbance2012; @postProximateStructuralMechanisms2007; @woottonOmnivoryStabilityFreshwater2017]. When omnivory is absent in three-species communities, the trophic structure or "motif" assumes a simple linear food chain with a maximum trophic position of three (**Figure 1D**). However, FCL decreases with increasing omnivory as the top predator eats lower in the food web [@wardMechanisticTheoryAquatic2017; @woottonOmnivoryStabilityFreshwater2017]. Theoretical work predicts that food webs are destabilized when omnivory is too strong, leading to the loss of species and shorter food chains [@woottonOmnivoryStabilityFreshwater2017]. Conversely, weak omnivory stabilizes the food web and increases the persistence of species within a community, particularly at intermediate levels of productivity and high disturbance levels [@woottonOmnivoryStabilityFreshwater2017; @woottonManyWeakInteractions2016]. Due to the context-dependency of FCL to multiple drivers and the potential for interactive effects, a unified framework of multiple FCL drivers is needed to better understand when and where FCL will respond to these extrinsic and intrinsic factors.

@@

We simulate trophic community dynamics within branching habitats to investigate the effects of extrinsic controls of FCL, such as ecosystem geometry [size (number of patches) and complexity (branching probability] and disturbance regime. In addition, our simulation model incorporates established intrinsic drivers of FCL, including the degree of omnivory, productivity level, and species' dispersal ability, allowing us to assess the context dependency on drivers of FCL. We find that ecosystem size and complexity are both positively related to FCL, but the form of this relationship is dependent on other extrinsic and intrinsic factors. Our model is an important step in unifying drivers of FCL across extrinsic and intrinsic drivers and parsing their context-dependency in spatially complex ecosystems.

@@

Thus, our definition accounts for the influence of omnivory. We defined the global FCL $\bar{\tau}$ across patches $N_p$ and time $T$ as $\bar{\tau} = \frac{\sum_x \sum_t \tau_{x,t}}{N_p T}$ (i.e., average over space and time).

@@

There were three consistent patterns in the relationship between FCL and ecosystem geometry (size and complexity). First, the effects of ecosystem size and complexity were modulated by disturbance. Second, productivity strengthened the relationship between FCL and ecosystem geometry with important direct effects that were motif dependent. Third, dispersal had a minimal but non-negligible positive effect on FCL. Below we describe these results in detail.

@@

Ecosystem geometry interacted with disturbance to dictate FCL in branching ecosystems (**Figures 2 and 3**). With no disturbance, both geometric features (size and complexity) had limited influence on FCL. However, as disturbance frequency increases, the relationships between FCL and ecosystem geometry become positive. This interactive effect emerged because the sensitivity of FCL to disturbance depended on ecosystem geometry. Although increased disturbance frequency reduced overall FCL, smaller and/or simpler ecosystems exhibited greater vulnerability (**Figures 2 and 3**). Therefore, disturbance interacted with ecosystem geometry to produce the interdependence of these factors in determining FCL. However, the maximum levels of FCL were strongly regulated by disturbance frequency, highlighting the important direct effect of disturbance. It is important to note that the interactive effects were not observed with low disturbance intensity (**Figures S3 and S4**); this suggests that disturbance intensity must be strong enough to be influential.

The exception is the chain scenario (no omnivory) with no disturbance and low productivity. In this scenario, ecosystem size had a positive effect on FCL (**Figure 2**), while ecosystem complexity had a negative influence (**Figure 3**). These opposing influences of ecosystem size and complexity were associated with their contrasting relationships with the total carrying capacity (i.e., carrying capacity summed across all patches): ecosystem size increased the total carrying capacity, whereas ecosystem complexity decreased it (**Figure S10**). However, these patterns characteristic of the chain scenario diminished when considering some levels of omnivory.

State transitions shed light on how FCL changes occurred. In the chain motif, an additive mechanism (i.e., the addition of higher trophic species) was always responsible for the changes in FCL. With disturbance, state transition occurs from "B" to "B + C" (low productivity) or "B + C" to "B + C + P" (high productivity) as ecosystem size or complexity increases (**Figures S5 and S6**). Exceptionally, the state transition of "B + C + P" $\rightarrow$ "B + C" occurred as ecosystem complexity increased with no disturbance and low productivity, a scenario in which ecosystem complexity decreased FCL.

In the weak and strong omnivory motifs, ecosystem size and complexity increased FCL through different mechanisms. Ecosystem size increased FCL primarily through additive mechanisms, facilitating the state transition of "B" $\rightarrow$ "B + P" (low productivity) or "No species" $\rightarrow$ "B + P" (high productivity), particularly with frequent disturbance (**Figure S5**). In contrast, insertion (i.e., the insertion of intermediate trophic species) and additive mechanisms were responsible for the effect of ecosystem complexity. With weak omnivory, the transition from "B + P" to "B + C + P" (insertion) was predominant when productivity was low (**Figure S6B**). However, the additive mechanism ("No species" $\rightarrow$ "B + P") took primacy in the high productivity scenario (**Figure S6B**). In the strong omnivory motif, transition patterns depended on disturbance frequency. When disturbance was rare ($p_m = 0.05$), the insertion mechanism ("B + P" $\rightarrow$ "B + C + P") drove the FCL change (**Figure S6C**). As disturbance frequency increased, the primary process switched to an additive mechanism ("B" $\rightarrow$ "B + P" or "No species" $\rightarrow$ "B + P"; **Figure S6C**).

## Productivity effect

High productivity strengthened the relationship between FCL and ecosystem geometry. In the chain motif, productivity greatly increased the overall FCL (**Figure S7**), thereby shifting the upper bound of FCL (**Figures 2 and 3**). In contrast, increased productivity decreased FCL with weak and strong omnivory (**Figures 2, 3, and S7**). This negative effect of increased productivity was apparent in smaller and/or simpler ecosystems, steepening the slopes between FCL and ecosystem geometry (**Figures 2 and 3**).

State transitions associated with increased productivity depended on the motif structure. In the chain motif, the transition from "B + C" to "B + C + P" was dominant regardless of disturbance frequency (**Figure S8**). The introduction of omnivory allowed the transition between "B + P" and "B + C + P". With weak omnivory, the transition of "B + C + P" $\rightarrow$ "B + P" was prevalent and shortened FCL across disturbance regimes (**Figure S8**). However, this transition was marginal in the strong omnivory motif. Instead, productivity significantly increased the proportion of the "No species" state (**Figure S8**) in disturbed scenarios, especially in small and/or simple ecosystems (**Figures S5 and S6**).

## Dispersal effect

Dispersal distance had a positive influence on FCL regardless of simulation scenarios (**Figure S7**). However, this direct effect was weak in comparison to other factors.

State transitions occurred through an additive (chain) or insertion mechanism (omnivory). In the chain motif, the transitions were either "B" $\rightarrow$ "B + C" or "B + C" $\rightarrow$ "B + C+ P", depending on disturbance frequency (**Figure S9**). In the omnivory motifs, the predominant transition was from "B + P" to "B + C + P" (**Figure S9**).

@@

## Acknowledgements

@@

## Author contributions

@@

# References

>>>>

---
title: "Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems"
output: 
  # word_document:
  #   reference_docx: "word_format.docx"
  pdf_document:
   latex_engine: xelatex
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
bibliography: references.bib
csl: https://www.zotero.org/styles/ecosphere
mainfont: Times New Roman
fontsize: 12pt
header-includes:
  \usepackage{lineno, textgreek}
  \linenumbers
---

@@

More recently, food web ecologists have begun to recognize that FCL rarely responds to a single driver, but instead is determined by interactions of extrinsic (external environmental conditions) and intrinsic factors (species and/or food web attributes). For example, @wardMechanisticTheoryAquatic2017 showed that FCL was more responsive to increasing productivity in large ecosystems than small ones, whereas FCL was more sensitive to size in low-productivity systems. Such context-dependent responses to extrinsic factors seem to be tightly coupled with the arrangement of trophic links within a food web. For example, omnivory (feeding at multiple trophic levels) is a strong intrinsic driver of FCL [@takimotoEffectsProductivityDisturbance2012; @postProximateStructuralMechanisms2007; @woottonOmnivoryStabilityFreshwater2017]. When omnivory is absent in three-species communities, the trophic structure or "motif" assumes a simple linear food chain with a maximum trophic position of three (**Figure 1D**). However, omnivory changes the trophic structure with important implications for food web persistence. For example, theoretical work predicts that food webs are destabilized when weak omnivory is coupled with strong intraguild predation, leading to the loss of intraguild prey and shorter food chains at high productivity levels [@woottonOmnivoryStabilityFreshwater2017; @takimotoEffectsProductivityDisturbance2012; @postProximateStructuralMechanisms2007]. Due to the context-dependency of FCL to multiple drivers and the potential for interactive effects, a unified framework of multiple FCL drivers is needed to better understand when and where FCL will respond to these extrinsic and intrinsic factors.

@@

We simulate trophic community dynamics within branching habitats to investigate the effects of extrinsic controls of FCL. In our study, extrinsic controls include ecosystem geometry [size (number of patches) and complexity (branching probability] and disturbance regime. In addition, our simulation model incorporates established intrinsic drivers of FCL, including the degree of omnivory, productivity level, and species' dispersal ability, allowing us to assess the context dependency on drivers of FCL. We find that ecosystem size and complexity are both positively related to FCL, but the form of this relationship is dependent on other extrinsic and intrinsic factors. Our model is an important step in unifying drivers of FCL across extrinsic and intrinsic drivers and parsing their context-dependency in spatially complex ecosystems.

@@

Thus, our definition accounts for the influence of omnivory. As a result, the FCL in a single patch can change due to the P's degree of omnivory and/or species extinction. We defined the global FCL $\bar{\tau}$ across patches $N_p$ and time $T$ as $\bar{\tau} = \frac{\sum_x \sum_t \tau_{x,t}}{N_p T}$ (i.e., average over space and time).

@@

There were three consistent patterns in the relationship between FCL and ecosystem geometry (size and complexity). First, both ecosystem size and complexity had positive effects on FCL when disturbance was strong and frequent (**Figure 2**). Second, in the absence of disturbance, their effects were highly dependent on motifs and productivity levels (**Figure 2**). Third, dispersal did not qualitatively alter the effects of ecosystem geometry, although it had non-negligible direct positive effect on FCL. Below we describe these results in detail.

@@

Ecosystem geometry interacted with disturbance to dictate FCL in branching ecosystems (**Figures 3 and 4**). In the presence of disturbance, both geometric features (size and complexity) had noticeable influences on FCL. As disturbance frequency increased, the relationships between FCL and ecosystem geometry became clearer and positive. This interactive effect emerged because the sensitivity of FCL to disturbance depended on ecosystem geometry. Although increased disturbance frequency reduced overall FCL, smaller and/or simpler ecosystems exhibited greater vulnerability (**Figures 3 and 4**). Therefore, disturbance interacted with ecosystem geometry to produce the interdependence of these factors in determining FCL. Yet, the interactive effects were not observed with low disturbance intensity (**Figures S3 and S4**); this suggests that disturbance intensity must be strong enough to be influential.

With no disturbance, the effects of ecosystem geometry were highly context dependent (**Figure 2**). In the chain scenario (no omnivory) with low productivity, ecosystem size had a positive effect on FCL (**Figure 3**), while ecosystem complexity had a negative influence (**Figure 4**). These opposing influences of ecosystem size and complexity were associated with their contrasting relationships with the total carrying capacity (i.e., carrying capacity summed across all patches): ecosystem size increased the total carrying capacity, whereas ecosystem complexity decreased it (**Figure S10**). However, when considering some levels of omnivory, these patterns characteristic of the chain scenario diminished. With weak omnivory (the second rows of **Figure 3 and 4**), ecosystem complexity had consistent positive effects on FCL, except the scenario with low productivity and short dispersal (**Figure 4**). In contrast, the effect of ecosystem size was more productivity dependent (**Figure 4**). Neither of ecosystem size and complexity influenced FCL with strong omnivory.

## State transitions

State transitions largely depended on motif structure and shed light on how FCL changes occurred. In the chain motif, an additive mechanism (i.e., the addition of higher trophic species) was always responsible for the changes in FCL. With disturbance, state transition occurs from "B" to "B + C" (low productivity) or "B + C" to "B + C + P" (high productivity) as ecosystem size or complexity increases (**Figures 5 and 6**). Exceptionally, the state transition of "B + C + P" $\rightarrow$ "B + C" occurred as ecosystem complexity increased with no disturbance and low productivity, a scenario in which ecosystem complexity decreased FCL.

In the weak and strong omnivory motifs, different state transitions were associated with ecosystem size and complexity. Ecosystem size increased FCL primarily through additive mechanisms, facilitating the state transition of "B" $\rightarrow$ "B + P" (low productivity) or "No species" $\rightarrow$ "B + P" (high productivity), particularly with frequent disturbance (**Figure 5**).

In contrast, insertion (i.e., the insertion of intermediate trophic species) and additive mechanisms were responsible for the effect of ecosystem complexity. With weak omnivory, the transition from "B + P" to "B + C + P" (insertion) was predominant when productivity was low (**Figure 6B**). However, the additive mechanism ("No species" $\rightarrow$ "B + P") took primacy in the high productivity scenario (**Figure 6B**). In the strong omnivory motif, transition patterns depended on disturbance frequency. When disturbance was rare ($p_m = 0.05$), the insertion mechanism ("B + P" $\rightarrow$ "B + C + P") drove the FCL change (**Figure 6C**). As disturbance frequency increased, the primary process switched to an additive mechanism ("B" $\rightarrow$ "B + P" or "No species" $\rightarrow$ "B + P"; **Figure 6C**).

<!-- ## Productivity effect -->

<!-- High productivity strengthened the relationship between FCL and ecosystem geometry. In the chain motif, productivity greatly increased the overall FCL (**Figure S7**), thereby shifting the upper bound of FCL (**Figures 2 and 3**). In contrast, increased productivity decreased FCL with weak and strong omnivory (**Figures 2, 3, and S7**). This negative effect of increased productivity was apparent in smaller and/or simpler ecosystems, steepening the slopes between FCL and ecosystem geometry (**Figures 2 and 3**). -->

<!-- State transitions associated with increased productivity depended on the motif structure. In the chain motif, the transition from "B + C" to "B + C + P" was dominant regardless of disturbance frequency (**Figure S8**). The introduction of omnivory allowed the transition between "B + P" and "B + C + P". With weak omnivory, the transition of "B + C + P" $\rightarrow$ "B + P" was prevalent and shortened FCL across disturbance regimes (**Figure S8**). However, this transition was marginal in the strong omnivory motif. Instead, productivity significantly increased the proportion of the "No species" state (**Figure S8**) in disturbed scenarios, especially in small and/or simple ecosystems (**Figures S5 and S6**). -->

<!-- ## Dispersal effect -->

<!-- Dispersal distance had a positive influence on FCL regardless of simulation scenarios (**Figure S7**). However, this direct effect was weak in comparison to other factors. -->

<!-- State transitions occurred through an additive (chain) or insertion mechanism (omnivory). In the chain motif, the transitions were either "B" $\rightarrow$ "B + C" or "B + C" $\rightarrow$ "B + C+ P", depending on disturbance frequency (**Figure S9**). In the omnivory motifs, the predominant transition was from "B + P" to "B + C + P" (**Figure S9**). -->

@@

# Acknowledgements

@@

# Author contributions

@@

\pagebreak

# References{-}

<div id="refs"></div>

\pagebreak

# Tables

```{r}
source(here::here("code/table_param.R"))

knitr::kable(df_value %>%
               dplyr::select(-"One-patch") %>% 
               rename(Value = "Main"),
             escape = FALSE,
             booktabs = TRUE,
             caption = "Parameter values used in the main simulation") %>% 
  kableExtra::kable_styling(latex_options = 'HOLD_position')
```

\pagebreak

# Figure captions

**Figure 1** (A) Example of simulated branching networks. Node color is reflective of the disturbance value calculated in network generation. (B) Density distributions of disturbance intensity (i.e., proportional reduction of a population). Three networks of 50 patches were produced with varied branching probabilities, which were shown in different colors. The vertical line indicates the mean disturbance intensity at headwaters ($\mu_m = 0.8$). (C) Schematic diagram of trophic interactions in a three-species community. $B$ refers to a basal species whose population level is controlled by a density-dependent function. The consumer species (or intraguild prey), $C$, consumes $B$ as a resource. The predator (or intraguild predator), $P$, is able to consume both $B$ and $C$. The structure and strength of these trophic interactions determined by functional responses. On the far left, a simple linear food chain exists when the predator does not consume the basal species. Moving to the right, basal species' biomass is converted to predator biomass at higher efficiencies with greater attack rates. (D) Proportional contribution of basal species $B$ to predator $P$ under different omnivory scenarios. The contribution changes with the relative density of $B$ to $C$ ($C=50$ in this example), and the rate of change is determined by attack rate and handling time.

**Figure 2** Relationships between food chain length and ecosystem size with high disturbance intensity $\mu_m = 0.8$. Lines indicate loess curves, and shades are associated 95% confidence intervals. Rows distinguish food web motifs, and columns indicate different dispersal and productivity scenarios. Different line colors indicate different disturbance probabilities.

**Figure 3** Relationships between food chain length and ecosystem complexity with high disturbance intensity $\mu_m = 0.8$. Lines indicate loess curves, and shades are associated 95% confidence intervals. Rows distinguish food web motifs, and columns indicate different dispersal and productivity scenarios. Different line colors indicate different disturbance probabilities.

**Figure 4** Relationships between patch state occupancy and ecosystem size with high disturbance intensity $\mu_m = 0.8$. Lines indicate loess curves, and shades are associated 95% confidence intervals. Panels indicate different food web motifs. In each panel, rows distinguish patch state, and columns indicate different dispersal and productivity scenarios. Different line colors indicate different disturbance probabilities.

**Figure 5** Relationships between patch state occupancy and ecosystem complexity with high disturbance intensity $\mu_m = 0.8$. Lines indicate loess curves, and shades are associated 95% confidence intervals. Panels indicate different food web motifs. In each panel, rows distinguish patch state, and columns indicate different dispersal and productivity scenarios. Different line colors indicate different disturbance probabilities.

### 2023-05-16 rmd/reply2.Rmd
edit: text

---
title: "RE: Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems"
output:
  pdf_document:
    latex_engine: xelatex
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
mainfont: Times New Roman
---

@@

> This is a great idea! We included a new hierarchical tree figure to show how different factors detemine the FCL response to ecosystem size/complexity (Figure 2 in the revised MS).
Also, we revised the figure captions to better guide readers.

@@

> Our unclear explanation may have confused the reviewer. There are a number of cases where all species (B, C, P) coexist. "*...is food chain length a product of the dynamic interactions that can be influenced by the magnitude of the trophic contributions from different trophic levels.*" This is how we defined FCL in our model, which was articulated in equations 12 & 13.

@@

> We appreciate your feedback. The figure captions were editted so the readers can better understand what those figures mean.
In particular, we have reworded the confusing term "occupancy" to "proportion of patch state" to clarify the y-axis.

@@

> Thank you, please let us clarify.
First, we defined FCL as trophic position, not as trophic level. Thus, the FCL can take continuous values.
With omnivory, the max is greater than 2 becuase of the coexistence of C and P.
P's trophic level depends on the relative abundance of B.
Thus, with omnivory, the FCL can be shorter than the chain motif even if the same set of species coexist.

@@

> Thank you for your input. "*Looking at the figure 1 c (and from experience) the expectation is that as omnivory increases the FCL decreases.*" -- The response of FCL to increasing omnivory can be more complex.
Weak omnivory can cause similar or even lower FCL than strong omnivory because the intraguild predator has a greater predation pressure on intraguild prey.
For the definition of FCL in our study, please see equations 12 & 13 -- it accounts for relative availability of B and C in a given habitat patch.

@@

> Thank you, we have revised figure captions.

@@

> Thank you! We have now added a color scale that indicate the relative reliance on B and C.
Meanwhile, we avoided to include FCL in the figure; this is because the relative reliance per se may not necessarily determine the FCL.
For example, weak omnivory could enhance the extirpation of intraguild prey, potentially resulting in a shorter FCL than that in strong omnivory.

@@

> Agreed -- there are two levels of productivity in our model, and this set up was unavoidable.
In the meantime, we feel that too much emphasis on this part may over-complicate the content, which is complex enough already (as you pointed out earlier in this round of review). In looking at the one-patch simulation, the FCL response to increased productivity can be well understood based on the single-patch analog. Thus, we decided not to delve into the specifics on this issue.

@@

> We are not sure if we correctly understood this comment, but we interpreted this comment suggesting to move the patch state figures to the maintext. We have now moved those figures to the maintext. In the meantime, we kept the text to explain those figures in the result section, since it seems inappropriate to mention those findings in the discussion section without mentioning them in the result.

@@

> We have defined the term in the Intro.

>>>>

---
title: "RE: Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems"
output:
  pdf_document:
    latex_engine: xelatex
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
mainfont: Times New Roman
fontsize: 12pt
---

@@

> This is a great idea! We included a new hierarchical tree figure to show how different factors determine the FCL response to ecosystem size/complexity (Figure 2 in the revised MS).
Also, we revised the figure captions to better guide readers.

@@

> Our unclear explanation may have confused the reviewer. There are a number of cases where all species (B, C, P) coexist. "*...is food chain length a product of the dynamic interactions that can be influenced by the magnitude of the trophic contributions from different trophic levels.*" This is how we defined FCL in our model, which was articulated in equations 12 & 13. The FCL can change due to (1) the P's degree of omnivory, and/or (2) species extinction. We have clarified these in the Method.

@@

> We greatly appreciate your input. We have made improvements to the figure captions in order to enhance reader comprehension regarding the meaning of the figures.

> Specifically, we have carefully edited the captions to provide a clearer understanding of the y-axis by replacing the confusing term "occupancy" with the more explicit phrase "proportion of patch state."

@@

> Thank you, please let us clarify.
We defined FCL as trophic position, not trophic level.
Thus, the FCL can take continuous values.
With omnivory, the max is greater than 2. This occurs when P and C coexist.
P's trophic level depends on the relative abundance of B and C (see equations 12 & 13).
Thus, with omnivory, the FCL is unavoidably shorter than the chain motif even if the same set of species coexist.

@@

> Thank you for your input. "*Looking at the figure 1 c (and from experience) the expectation is that as omnivory increases the FCL decreases.*" -- The response of FCL to increasing omnivory can be more complex.
Weak omnivory can cause similar or even lower FCL than strong omnivory because the intraguild predator can have a greater predation pressure on intraguild prey (due to higher attack rate to C).
For the definition of FCL in our study, please see equations 12 & 13 -- it accounts for relative availability of B and C in a given habitat patch.
Please see also our response to your earlier comments.

@@

> Thank you, we have revised figure captions.
Specifically, we have carefully edited the captions to provide a clearer understanding of the y-axis by replacing the confusing term "occupancy" with the more explicit phrase "proportion of patch state."

@@

> Thank you. We have now added a color scale that indicates the relative reliance on B and C.
Meanwhile, we avoided to include FCL in the figure; this is because the relative reliance per se may not necessarily determine the FCL.
For example, weak omnivory could enhance the extirpation of intraguild prey, potentially resulting in a shorter FCL than that in strong omnivory.

@@

> We appreciate your understanding regarding the two levels of productivity in our model

> However, we feel that placing excessive emphasis on this particular aspect might further complicate an already complex content, as you astutely pointed out earlier during this round of review.

> Upon analyzing the one-patch simulation, we found that the response of the FCL to increased productivity at the network level aligned well with that of a single-patch system.
Consequently, we made a decision not to delve into the specifics of this issue.
Thank you for your valuable insights though!

@@

> We are uncertain if we have fully grasped the intended meaning of this comment, but our understanding is that it suggests relocating the patch state figures to the main text. Consequently, we have moved these figures to the main body of the manuscript.

> Simultaneously, we have retained the accompanying text that explains the figures in the results section. This decision was made because it would be inappropriate to discuss these findings in the discussion section without prior mention of them in the results section.

> Thank you for bringing this matter to our attention, and we apologize for any confusion or misinterpretation that may have arisen.

@@

> Thank you. In the previous version of the manuscript, we have introduced "ecosystem geometry" as the term including ecosystem size and complexity in the Introduction. However, it was probably difficult to find. We have re-worded so the readers can find the information more easily.
